Bluetooth Loader for mruby Bytecode \\ in Multi-VM Environment

### 2016-04-08 EMSOFT2016/diff/0407_thesis.tex
update

\subsection{Synchronization of multiple RiteVM tasks}
To execute mulitiple mruby applications, synchronization mechanism of RiteVM tasks is supported in the proposed framework.
We measured the time from first RiteVM task executing to last RiteVM task executing, and confirm that the time is within (periodic time)$\times$(the number of RiteVM tasks $-$ 1).
%The cases that the number of RiteVM tasks is two, three, and four 
Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
The periodic time is one msec, and the number of RiteVM is four.
The time is within three msec as shown in Figure \ref{fig:eval_synchronization}, which shows synchronization of multiple RiteVM tasks is performed.

>>>>

\subsection{Synchronization of multiple RiteVM tasks}
To execute mulitiple mruby applications, synchronization mechanism of RiteVM tasks is supported in the proposed framework.
We measured the time from first RiteVM task executing to last RiteVM task executing, and confirm that the time is within (periodic time)$\times$(the number of RiteVM tasks $-$ 1).
Figure \ref{fig:eval_synchronization} shows the cases where the number of RiteVM tasks is two, three, and four.
% Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
The periodic time is one msec.
The time is within one msec, two msec, and three msec respectively as shown in Figure \ref{fig:eval_synchronization}, which shows synchronization of multiple RiteVM tasks is performed.
